\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-08-04 forwards-and-backwards.tex
tightness

% % % % % % % % %
\begin{theorem}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
The collection of measure-valued processes 
$\{(\eta^{N}_t)_{t \geq 0}: \theta > 0\}$
is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
\end{theorem}
\begin{proof}
To prove relative compactness 
of the processes $(\eta^{N}_t)_{t \geq 0}$,
we apply Theorem 3.9.1. in \cite{EK}.

First of all, the set of measures 
$\{ \mu: \langle 1, \mu \rangle \leq K \} $
is compact in $\mathcal{M}_F(\overline{\mathbb{R}^d})$.
Therefore, by Lemma \ref{lem:eta_compact_containment},
our processes satisfy the compact containment condition.

Secondly, the set of functions $\mathcal{C}^{2}_{0}(\overline{\mathbb{R}^d})$ is a dense subset of all continuous functions on $\mathcal{M}_f(\overline{\mathbb{R}^d})$
under the topology of uniform convergence in compact sets.

Furthermore,
since each measure $\eta^{N}_t$ is concentrated in $\mathbb{R}^d$,
it suffices to show that the real-valued processes
$\langle f, \eta^{N}_t \rangle$
is tight for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$,
which is proven in
Theorem \ref{lem:eta_projections_tightness}.
\end{proof}

>>>>

% % % % % % % % %
\begin{theorem}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
    The collection of measure-valued processes 
    $\{(\eta^{N}_t)_{t \geq 0}: N > 0\}$
    is tight in $\mathcal{D}_{[0,\infty)}(\measures)$.
\end{theorem}

\begin{proof}
    Theorem 3.9.1~in \cite{EK},
    says that if the collection of $E$-valued processes
    satisfies a compact containment condition
    (for any $\epsilon > 0$ and $T>0$, there is a compact set
    such that the processes stay within that set up to time $T$ with probability at least $1-\epsilon$),
    then the collection is relatively compact
    if and only if
    $\{(f(\eta^{N}_t))_{t \geq 0}: N > 0\}$ is relatively compact
    for all $f$ in a dense subset of $C_0(E)$
    under the topology of uniform convergence in compact sets.

    First of all,
    the set of measures $\{ \mu: \langle 1, \mu \rangle \leq K \} $ is compact in $\cmeasures$,
    so Lemma \ref{lem:eta_compact_containment}
    shows that our processes satisfy a compact containment condition.
    Secondly, Lemma \ref{lem:eta_projections_tightness}
    shows that the real-valued processes $\langle f, \eta^{N}_t \rangle$
    are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
    Since the set of finite sums and products of terms of this form
    is dense in the space of bounded continuous functions on $\cmeasures$,
    we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
    Finally,
    since each measure $\eta^{N}_t$ is concentrated in $\IR^d$,
    any limit point must in fact be in $\measures$,
    and so we have 
    tightness in $\mathcal{D}_{[0,\infty)}(\measures)$.
\end{proof}
